Optimizing the Cobb Doughlas Habitability Production function using Particle Swarm Optimization

### 2017-11-27 docs/report/draft.tex
Added pointers to draft.
Finished introduction in report.

\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}

@@

@@

\begin{abstract}
  Write a super cool abstract here.
\end{abstract}

\section{Introduction}
What am I trying to do?\\

\begin{pointers}
\item What is CDHPF?\ Why use a metric?
\item Previous attempts.
\item What is PSO?\
\item Why PSO?\
\item Overview of paper.
\end{pointers}

\section{Cobb Douglas Habitability Score}
\begin{pointers}
\item A little background (expanding from Introduction).
\item The equations.
\item Method for calculating the score.
\end{pointers}

\section{Particle Swarm Optimization}
\begin{pointers}
\item Equations. Modification for max.
\item Constrained optimization modifications.
\item Any other changes made.
\item Algorithm: Putting everything together.
\end{pointers}

>>>>

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{mathtools}

@@

% Useful replacements.
\newcommand{\pso}{Particle Swarm Optimization}

@@

\section{Introduction}
% Note to self, improve the flow of the report.
% Find citations.
Under most paradigms, optimization of a continuous function requires the calculation of a gradient. This might not
always be feasible for non-polynomial functions in high-dimensional search spaces. This is further complicated when the
optimization must be performed under constraints. \pso\ is a metaheuristic for continuous function optimization that does
away with the need for a gradient. It employs a large number of particles that traverse the search space converging
toward a global best solution encountered by at least one of the particles.

\pso\ is a distributed method that requires simple mathematical operators and few lines of code, making it a lucrative
solution where computation resources are at a premium. Its implementation is highly parallelizable. It scales with the
dimensionality of the search space. Constrained optimization can be incorporated within the standard algorithm through
the use of a penalty function.

% Pull out citations from the Applications paper.
\pso\ has been successfully adapted to a wide range of design optimization problems, e.g., networks and VLSI design.
\pso\ has also found applications in machine learning under clustering, feature detection and classification.  As a
modelling paradigm, it has been used for constructing customer satisfaction models, MIDI music models, friction models,
etc.

In this paper, \pso\ has been applied to estimate the Cobb Douglas Habitability Score of an exoplanet. The score is
estimated by maximizing the Cobb-Douglas Habitability Production Function. The function considers four parameters,
radius, mass, escape velocity and surface temperature, taken from the Exoplanets Catalog hosted by the Planetary
Habitability Laboratory, UPR Arecibo. Since the Cobb-Douglas function is concave under certain constraints, the
problem can be reduced to a convex optimization over the negative of the production function.

\section{Cobb-Douglas Habitability Score}

\subsection{Cobb-Douglas Habitability Production Function}
The general form of the Cobb-Douglas production function is given by,
\begin{equation}
  Y = k\cdot{(x_1)}^\alpha\cdot{(x_2)}^\beta,
\end{equation}
where $k$ is a constant that may be set according to requirement, $x_1$ and $x_2$ are the input parameters to the
function, $Y$ is the total output production value, and $\alpha$ and $\beta$ are called the elasticity coefficients.

% \begin{pointers}
% \item Describe the Cobb Douglas Habitability Score.
% \item Describe CRS, DRS and IRS\@.
% \item Splitting the CDHS score into two values.
% \item State the equations.
% \item Score is estimated by maximizing the CDHPF fn.
% \end{pointers}

\section{Particle Swarm Optimization}
\begin{pointers}
\item Equations. Modification for max.
\item Constrained optimization modifications.
\item Algorithm for PSO\@.
\end{pointers}
